---
title: "Chapter 8"
author: "Mark Dunning"
date: "2 October 2014"
output: html_document
---

# Controlling Code chunks

##Include

Use `include = FALSE` when you want code to be executed, but not display the code or the execution results. 

e.g. *you want to set some formatting options for the document*

```{r include=FALSE}
options(digits = 3,width=100)
```

##eval

Use `eval=FALSE` when you want to display some formatted R code, but not actually run.

e.g. *you want to give some copy-and-paste instructions to the user, but not run it as part of your script*


```{r eval=FALSE}
?options
install.packages("ggplot2")
```

##echo

Use `echo=FALSE` if you want the consequences of the code to be displayed, but not the code itself.

e.g. *you are share an analysis script with a collaborator, but don't want to expose them to the gory details of how the plots were created*

>Here is an excellent plot of two randomly-generated vectors
```{r echo=FALSE}
x <- runif(100,0,1)
y <- runif(100,1,2)
plot(x,y,ylim=c(0,2))
```

##results

e.g. *the code you are running produces lots of annoying print statements*

```{r results='hide'}
coins <- NULL

for(i in 1:100){
  
  mycoin <- rbinom(1,1,0.5)
  ifelse(mycoin, print("Heads"), print("Tails"))
  coins[i] <- mycoin
}
```

```{r}
table(coins)
```



##warning, message

```{r warning=FALSE,message=FALSE}
library(beadarray)
```


#in-line code